\documentclass[11pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{amsmath,amssymb,amsthm,enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{fancyhdr} 

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}

\setlist[description]{style=multiline,leftmargin=1.25cm,parsep=0pt,itemsep=.0in}
\newlength\listindent
\setlength\listindent{4in}


\lhead{}
\rhead{\hspace{-1in} }
\lfoot{}
\cfoot{\thepage}
\rfoot{}

% Set your name here
\def\name{Taylor Jaworski}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economic history, industrial organization,
    expeirmental economics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\renewcommand{\descriptionlabel}[1]{\hspace{\labelsep}\textsf{#1}}

% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}
%\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\normalsize\bf}
\subsectionfont{\rmfamily\mdseries\itshape\normalsize}

% Don't indent paragraphs.
\setlength\parindent{.0in}

% Make lists without bullets and compact spacing
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0in}
    \setlength{\itemsep}{.0in}
    \setlength{\parskip}{0in}
    \setlength{\parsep}{0in}
	\setlength{\itemindent}{.25in}
  }
}{
  \end{list}
}


\textwidth = 6.5 in
\textheight = 9 in
\topmargin = 0in
\oddsidemargin = 0in
\marginparsep = 0in
%\headheight = .5in

\begin{document}

\textbf{\LARGE Taylor Jaworski} {\scriptsize(\textbf{Updated:} \today) }


{ Address: University of Colorado, Department of Economics--UCB 256, Boulder, CO, 80309} \vspace{.25em} \\ 
{ Email: \href{tjaworski@nber.org}{\color{black} \tt tjaworski@nber.org}, Website: 
\href{https://jaworskit.github.io/}{\color{black} \tt jaworskit.github.io}, Office:
{\color{black}\tt +1 303-492-2650}}

\vspace{-1em}
\section*{Current employment and affiliations}

\begin{description}[leftmargin=.75in,itemsep=.25em,itemindent=0in]
	\item[2017 - ] University of Colorado, Boulder
	\item[]			\hspace{.1in}Dept of Economics: Assistant Professor
	\item[]			\hspace{.1in}Affiliate: Dept of History, Center of the American West, Center for Western Civ
	\item[2016 - ]	National Bureau of Economic Research
	\item[]			\hspace{.1in}Faculty Research Fellow: Development of the American Economy
\end{description}

\vspace{-1em}
\section*{Previous positions}

\begin{description}[leftmargin=.75in,itemsep=.25em,itemindent=0in]
	\item[2014 - 17] 	Queen's University, Dept of Economics, Assistant Professor
	\item[2008 - 09] 	Chapman University, Economic Science Inst, Research Associate
\end{description}

\vspace{-1em}
\section*{Education}

\begin{description}[leftmargin=.75in,itemsep=.25em,itemindent=0in]
  	\item[2009 - 14] 	University of Arizona, PhD in economics 
 	\item[2007 - 08] 	London School of Economics, MSc in economic history 
  	\item[2003 - 07] 	George Washington University, BA in economics \& international affairs 
 	\item[2005 - 06] 	London School of Economics, General Course in economics \& history 
\end{description}

\vspace{-1em}
\section*{Accepted and published papers in refereed journals}

\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=.15in]
\item 	``\href{https://doi.org/10.1016/j.eeh.2020.101343}{\color{black}
			Specification and Structure in Economic History},'' 
			\emph{Explorations in Economic History}, Vol. 77, No. 3 (July 2020), pp. 1--10.
\item 	``\href{https://doi.org/10.1162/rest_a_00808}{\color{black}
			National Policy for Regional Development: Historical Evidence from Appalachian Highways},'' 
			with Carl Kitchens, \emph{Review of Economics \& Statistics}, Vol. 101, No. 5 (December 2019), pp. 777--790.
\item 	``\href{https://doi.org/10.1111/ehr.12430}{\color{black}
			Shakeout in the Early Airframe Industry},'' 
			with Andrew Smyth, \emph{Economic History Review}, Vol. 71, No. 2 (May 2018), pp. 617--638.
\item 	``\href{https://doi.org/10.1080/01615440.2017.1393360}{\color{black}
			Revisiting the Great Compression},'' 
			with Gregory T. Niemesh, \emph{Historical Methods}, Vol. 51, No. 1 (March 2018), pp. 39--48.
\item 	``\href{https://doi.org/10.1080/13504851.2017.1355531}{\color{black}
			Entry and Pricing on Broadway},'' with Maggie Jones and Mario Samano, 
			\emph{Applied Economics Letters}, Vol. 25, No. 10 (March 2018), pp. 653--658.
\item 	``\href{https://doi.org/10.1017/S0022050717000791}{\color{black}
			World War II and the Industrialization of the American South},'' 
			\emph{Journal of Economic History}, Vol. 77, No. 4 (December 2017), pp. 1048--1082.
\item 	``\href{https://doi.org/10.1016/j.eeh.2016.05.002}{\color{black}
			Ownership and the Price of Residential Electricity: Evidence from the United States, 1935-1940},'' 
			with Carl Kitchens, \emph{Explorations in Economic History}, Vol. 64, No. 2 (April 2017), pp. 53--61.
\item 	``\href{https://doi.org/10.1111/iere.12151}{\color{black} 
			Bubbles, Crashes and Endogenous Uncertainty in Linked Asset and Product Markets},'' 
			with Erik O. Kimbrough, \emph{International Economic Review}, Vol. 57, No. 1 (February 2016), pp. 155--176.
\item 	``\href{https://doi.org/10.1017/S0022050714000060}{\color{black} 
			`You're in the Army Now': The Impact of World War II on Women's Education, Work, and Family},'' 
			\emph{Journal of Economic History}, Vol. 74, No. 1 (March 2014), pp. 169--195.		
\item 	``\href{https://doi.org/10.4284/0038-4038-2011.249}{\color{black}
			Go West Young Man: Self-Selection and Endogenous Property Rights},'' 
			with Bart J. Wilson, \emph{Southern Economic Journal}, Vol. 78, No. 2 (April 2013), pp. 886--904.
\item 	``\href{https://doi.org/10.1515/jbwg-2014-0011}{\color{black}
			Health on the Home Front: Infant Deaths and Industrial Accidents During Mobilization for World War II},'' 
			with Price V. Fishback, \emph{Jahrbuch f\"{u}r Wirtschaftsgeschichte} [\emph{Economic History Yearbook}] No. 2 (2014), pp. 15--30.
\item 	``\href{https://doi.org/10.1093/jleo/ewr024}{\color{black}
			The Ecological and Civil Mainsprings of Property: An Experimental Economic History of Whalers' Rules of Capture},'' 
			with Bart J. Wilson, Karl Schurter, and Andrew Smyth, 
			\emph{Journal of Law, Economics, and Organization}, Vol. 28, No. 4 (October 2012), pp. 617--656.
\item 	``\href{https://doi.org/10.1016/S1477-3880(15)30053-0}{\color{black}
			Discovering Economics in the Classroom with Experimental Economics and the Scottish Enlightenment},'' 
			with Vernon L. Smith, and Bart J. Wilson, \emph{International Review of Economics Education}, Vol. 9, No. 2 (2010), pp. 10--33.
\end{description}

\vspace{-1em}
\section*{Book chapters}

\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=.15in]
\item 	``\href{https://doi.org/10.1017/S0022050717000791}{\color{black}
			Two World Wars in American Economic History},'' 
			with Price V. Fishback, in \emph{Oxford Handbook of American Economic History}, 
			eds. Louis P. Cain, Price V. Fishback, and Paul Rhode, Vol. 2 (2018), pp. 391--418. 
\item 	``\href{https://doi.org/10.1007/978-981-10-1605-9_9}{\color{black}
			World War II and US Economic Performance},'' 
			with Price V. Fishback, in \emph{Economic History of Warfare and State Formation},
			eds. Jari Eloranta, Eric Golson, Andrei Markevich, and Nikolaus Wolf (2016), pp. 221--241. 
\end{description}

\vspace{-1em}
\section*{Book reviews}

\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=.15in]
\item 	\href{https://doi.org/10.1017/S0022050717000432}{\color{black}
			Review of Mark R. Wilson's \emph{Destructive Creation: American Business and the Winning of World War II}}, 
			\emph{Journal of Economic History}, Vol. 77, No. 2 (June 2017), pp. 629--630.
\item 	\href{https://doi.org/10.1017/S0007680517000897}{\color{black}
			Review of John L. Neufeld's \emph{Selling Power: Economics, Policy, and Electric Utilities Before 1940}}, 
			\emph{Business History Review}, Vol. 91, No. 2 (Summer 2017), pp. 420--422.	
\item 	\href{https://doi.org/10.1111/ehr.12325}{\color{black} 
			Review of Bruce Smardon's \emph{Asleep at the Switch: The Political Economy of Federal Research and Development Policy since 1960}}, 
			\emph{Economic History Review}, Vol. 69, No. 1 (February 2016), pp. 406--407.
\item 	\href{https://doi.org/10.1017/S0022050713000168}{\color{black} 
			Review of Paul A.C. Koistinen's \emph{State of War: The Political Economy of American Warfare, 1945-2011}}, 
			\emph{Journal of Economic History}, Vol. 73, No. 1 (March 2013), pp. 297--298.
\item 	\href{https://doi.org/10.1017/S0022050712000800}{\color{black} 
			Review of Hugh Rockoff's \emph{America's Economic Way of War: War and the US Economy from the Spanish-American War to the Persian Gulf War}}, 
			\emph{Journal of Economic History}, Vol. 72, No. 4 (December 2012), pp. 1108--1109.
\end{description}

\vspace{-1em}
\section*{Non-refereed publications}
\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=.15in]
\item ``\href{https://voxeu.org/article/globalisation-and-value-domestic-highway-infrastructure}{\color{black}
		Globalization and the value of domestic highway infrastructure},''	
		with Carl Kitchens and Sergey Nigai, \emph{VoxEU}, November 1, 2020.
				
\item ``\href{https://voxeu.org/article/innovation-spillovers-and-market-structure}{\color{black}
		Innovation spillovers and market structure: Evidence from the interwar aircraft industry},'' 
		with Walker Hanlon, \emph{VoxEU}, January 31, 2020.
	
\item ``\href{https://voxeu.org/article/wwii-and-industrialisation-american-south}{\color{black}
		WWII and the industrialisation of the American South},'' 
		\emph{VoxEU}, June 17, 2017.	
	
\item 	``\href{https://doi.org/10.1017/S0022050717000791}{\color{black}
			The Warring Forties: The Economic Consequences of World War II},'' 
			\emph{Journal of Economic History}, Vol. 75, No. 2 (June 2015), pp. 536--539. Dissertation Summary.
\end{description}

\vspace{-1em}
\section*{Working papers}

\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=.15in]
\item ``Openness to Trade and the Spread of Industrialization: Evidence from Canada during the First Era of Globalization,'' with Ian Keay, August 2020 (revise and resubmit at the \emph{Journal of Economic History}).

\item ``Spillover Effects of Intellectual Property Protection in the Interwar Aircraft Industry,'' with Walker Hanlon, August 2020 (under review).

\item ``Highways and Globalization,'' with Carl Kitchens and Sergey Nigai, October 2020.

%\item ``Subsidizing Entry in Retai}l Electricity Markets: The Competitive Effects of the New Deal's Rural Electrification Administration,'' with Carl Kitchens, August 2019
\end{description} 

\vspace{-1em}
\section*{Work in progress}

\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=.15in]
\item ``The Regional Effects of Regional Trade Agreements,'' with Carl Kitchens and Sergey Nigai
\item ``The Race Between Internal and External Integration,'' with Carl Kitchens and Sergey Nigai
\item ``US Labor Market Integration, 1940--2000,'' with Dominick Bartelme and Pinghui Wu
%\item 	``State Policies for Industrial Recruitment,'' with Carl Kitchens
%\item 	``Highways and Interwar Productivity Growth,'' with Carl Kitchens
\item 	``Bell Labs, Team Size, and Innovation,'' with Andrew Smyth
\item 	``US Regional Cultures,'' with Erik Kimbrough
\end{description} 

\vspace{-1em}
\section*{Funding}

\begin{description}[leftmargin=.75in,itemsep=.25em,itemindent=0in]
\item[2015]			Arthur H. Cole Grants-in-Aid, Economic History Association%, \$5,000
\item[2015]			Research Grant, Senate Advisory Research Committee, Queen's Univ%, \$7,000
\item[2013 - 14] 	Research Grant, McGuire Center, Univ of Arizona%, \$2,500
\item[2012 - 14] 	Doctoral Dissertation Improvement Grant, National Science Foundation%, \$9,900
\item[2011] 		Travel Grant, Economic History Association%, \$2,500
\item[2009 - 11] 	Research Grant, Intl Foundation for Research in Experimental Econ%, \$6,600
\end{description}

\vspace{-1em}
\section*{Fellowships, awards, and invited lectures}

\begin{description}[leftmargin=.75in,itemsep=.25em,itemindent=0in]
\item[2020]			Exceptional Referee Award, \emph{Journal of Economic History}
\item[2016]			Epstein Lecture, London School of Economics, Dept. of Economic History
\item[2014]			Finalist, Allan Nevins Prize, Economic History Association
\item[2014] 		IPUMS-USA Research Award for best graduate student paper in 2013
\item[2012 - 13] 	John E. Rovensky Fellowship, University of Illinois Foundation%, \$10,000
\item[2012] 		Oliver E. Williamson Prize for best article accepted in \emph{JLEO} in 2011
\item[2008] 	 	Hunt Prize, London School of Economics, Dept. of Economic History
\end{description}

\vspace{-1em}
\section*{Teaching}

\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=0in]
\item 	University of Colorado, Boulder: Economic History of North America (Econ 8534, graduate,$\times 1$), Economic History of the Europe (Econ 4514, undergraduate,$\times 1$), Economic History of the United States (Econ 4524, undergraduate,$\times 5$), Introduction to Econometrics (Econ 4818, undergraduate,$\times 1$)

\item 	Queen's University: Undergraduate Econometrics ($\times 2$), Undergraduate Economic History ($\times 3$), Graduate Empirical Methods ($\times 1$), PhD Workshop ($\times 2$)
\end{description}

\vspace{-1em}
\section*{Seminars and conference presentations {\footnotesize\bf{(scheduled in \emph{italics})}}}

\begin{description}[leftmargin=.75in,itemsep=.25em,itemindent=0in]
\item[2020 - 21] \underline{Seminars:} \emph{UC-Davis (Virtual)}

\item[2019 - 20] \underline{Seminars:} {Harvard Business School}, Auburn, Yale \underline{Conferences:} Urban Economics Association conference
	
\item[2018 - 19] \underline{Seminars:} Bristol, Warwick, Oxford, George Mason, Arizona \underline{Conferences:} NBER Summer Institute (DAE), Economic History Association conference, Mountain West Economic History conference

\item[2017 - 18] \underline{Seminars:} Michigan, UC-Santa Barbara \underline{Conferences:} NBER Spring Meetings (DAE)

\item[2016 - 17] \underline{Seminars:} Marquette, CU-Boulder, Chapman, Calgary, Florida State, Yale 

\item[2015 - 16] \underline{Seminars:} Lakehead, McGill, York \underline{Conferences:} NBER Summer Institute (DAE), UT-Knoxville conference, Colgate conference, Canadian Network for Economic History conference, Economic History Association conference 

\item[2014 - 15] \underline{Seminars:} Rensselaer, HEC Montreal, Colgate \underline{Conferences:} Vanderbilt conference, Cliometric Society conference, Middlebury  conference, Canadian Network for Economic History conference
\end{description}

\vspace{-1em}
\section*{Professional and service activities}

\begin{description}[leftmargin=0in,itemsep=.25em,itemindent=0in]

\item University of Colorado, Boulder: PhD placement director (2017--present, econ dept), PhD admissions committee (2017--2019, econ dept), hiring committee (2019-2020, econ dept), Planning Committee of the Arts and Sciences Council (2017--2018, university) 

\item Economic History Association: virtual seminar committee (2021), local arrangements committee (2020-2021), committee on research in economic history (2020--2023), conference program committee chair (2018--2019)

\item Queen's University: economic history workshop co-organizer (2014--2017, econ dept), Weatherall and invited speakers committee (2014--2017, econ dept), appointments committee (2015--2016, econ dept), JDI/QED conference organizer (May 2016, econ dept); PhD examiner for Koray Sayili (Queen's, business, 2016), Carl Skogstad (Queen's, economics, 2014)

%\item Canadian Network for Economic History: conference co-organizer (Oct 2015)

\item PhD Supervision: Brian Marein (Colorado, co-advisor), Matthew Hurt (Colorado, advisor), Peiyuan Li (Colorado, committee member), Kyle Butts (Colorado, committee member), Loren Kruschke (Colorado, committee member),  Andrea Craig (Queen's, co-advisor, completed: 2019, current: UBC-Okanagan, first placement: Windsor), Maggie Jones (Queen's, co-advisor, completed: 2018, first placement:  Victoria), Sergei Shibaev (Queen's, committee member, completed: 2017, first placement: Citi)

\item Master's Thesis: Eliane Barker (Queen's, 2016),  Stanley Wu (Queen's, 2016), Daniel Letcher (Queen's, 2016), Yang Xu (Queen's, 2015), Kathryn Conway (Queen's, 2015)

\item Undergraduate Thesis: Benjamin Potter (Colorado, 2020), John Stafford (Colorado, 2019), Rebecca Landau (Colorado, 2018) % Harrison Pearl (Colorado, 2020), 

\item Discussant: American Economic Association meetings (Jan 2021), Urban Economics Association conference (Oct 2019), Graduate Student Workshop of the Institute for the Study of Religion, Economics, and Society (May 2018, May 2019), Economic History Association meetings (Sept 2016), American Economic Association meetings (Jan 2015),

\item Refereeing: \emph{American Economic Journal: Applied Economics}, \emph{American Economic Review}, \emph{Demography}, \emph{Economic History Review}, \emph{Economic Inquiry}, \emph{Economic Journal}, \emph{Econometrica}, \emph{Experimental Economics}, \emph{Explorations in Economic History}, \emph{European Review of Economic History}, \emph{Historical Methods}, \emph{Journal of Development Economics}, \emph{Journal of Economic History}, \emph{Journal of Economics \& Management Strategy}, \emph{Journal of Human Resources}, \emph{Journal of Urban Economics}, National Science Foundation, Oxford University Press, \emph{Review of Economics \& Statistics}, \emph{Social Science History}, \emph{Southern Economic Journal} 

\item Member: American Economic Association, Cliometric Society, Economic History Association, Economic History Society
\end{description}

\vspace{-1em}
\section*{Public engagement}

\begin{description}[leftmargin=.75in,itemsep=.25em,itemindent=0in]

\item[Mar 2021] Panel on the political, economic, and social ideas of Alexander Hamilton and their representation in the Hamilton musical.

\item[Oct 2019] Panel on transportation in history with the Center of the American West at the University of Colorado, Boulder.

\item[Apr 2019] Interview with \emph{Mountain Money} on my work related to the economics of World War II (aired on the NPR affiliate KPCW in Park City, Utah).

\item[Dec 2018] Interview with blog \emph{explatalachians} written up under ``The Promise and Peril of an Appalachian New Deal.''
\end{description}

%\vspace{.5in}

%\textbf{Updated:} \today

\end{document}



